### 2023-11-08 manuscript.tex
Added more TODO notes to manuscript

\section{Results}
\subsection{IDRs are shorter and more divergent than non-disordered regions}
We identified regions with high levels of inferred intrinsic disorder in over 8,500 alignments of single copy orthologs from 33 species in the \textit{Drosophila} genus using the disorder predictor AUCPreD~\cite{Wang2016}. To highlight the unique features of IDR evolution in subsequent analyses, we also extracted a complementary set of regions with low levels of inferred disorder. Both sets were filtered on several criteria, including the lengths of their sequences and their phylogenetic diversity, which yielded 11,445 and 14,927 regions, respectively, from 8,466 unique alignments. In the subsequent discussion, we refer to these sets as the ``disorder'' and ``order'' regions, respectively. To investigate the differences in basic sequence statistics between the two region sets, we first generated histograms from the average length of each region (Fig.~\ref{sfig:regions}). Although both distributions span several orders of magnitude, the order regions are generally longer than the disorder regions, with means of 105 and 245 residues, respectively. We then quantified the sequence divergence in each region by fitting phylogenetic trees to the alignments using amino acid and indel substitution models. The average rates of substitution are significantly larger in the disorder regions, demonstrating that while both sets contain conserved and divergent regions, IDRs are enriched in more rapidly evolving sequences (Fig.~\ref{sfig:regions}). We also searched the database of Pfam domains against the full-length \textit{D. melanogaster} proteins in these alignments and measured their overlap with the disorder and order regions. The results show a clear enrichment in the disorder regions having no or only small amounts of overlap relative to the order regions, indicating that, relative to structured domains, IDRs are especially resistant to homology-based methods of functional annotation (Fig.~\ref{sfig:pfam}).

@@

\subsection{Future evolutionary analyses of IDRs will require a multimodal approach}
As discussed by Zarin \textit{et al.}, the interpretation of evolutionary signatures is complicated by several methodological limitations~\cite{Zarin2019}. For example, because IDRs are identified as contiguous segments of high predicted disorder, their boundaries are defined by adjacent structural elements. This approach can therefore split an IDR that is a single evolutionary or functional unit if it contains a semi-disordered module that scores below the threshold. Conversely, it can also merge two distinct IDRs if they are not separated by at least one folded domain. Another challenge is the significant overlap in the definitions of many features induces strong correlations that preclude straightforward quantitative manipulations or interpretations of an IDR's evolutionary signature. The original authors have since addressed this in subsequent studies by applying machine learning methods to perform feature selection or learn features directly from alignments of IDRs~\cite{Zarin2021, Lu2022}. However, integrating these methods into a unified phylogenetic comparative framework will require further effort.

>>>>

\section{Results}
\subsection{IDRs are shorter and more divergent than non-disordered regions}
% TODO: Add more explanation of origin of alignments here and in methods if necessary
We identified regions with high levels of inferred intrinsic disorder in over 8,500 alignments of single copy orthologs from 33 species in the \textit{Drosophila} genus using the disorder predictor AUCPreD~\cite{Wang2016}. To highlight the unique features of IDR evolution in subsequent analyses, we also extracted a complementary set of regions with low levels of inferred disorder. Both sets were filtered on several criteria, including the lengths of their sequences and their phylogenetic diversity, which yielded 11,445 and 14,927 regions, respectively, from 8,466 unique alignments. In the subsequent discussion, we refer to these sets as the ``disorder'' and ``order'' regions, respectively. To investigate the differences in basic sequence statistics between the two region sets, we first generated histograms from the average length of each region (Fig.~\ref{sfig:regions}). Although both distributions span several orders of magnitude, the order regions are generally longer than the disorder regions, with means of 105 and 245 residues, respectively. We then quantified the sequence divergence in each region by fitting phylogenetic trees to the alignments using amino acid and indel substitution models. The average rates of substitution are significantly larger in the disorder regions, demonstrating that while both sets contain conserved and divergent regions, IDRs are enriched in more rapidly evolving sequences (Fig.~\ref{sfig:regions}). We also searched the database of Pfam domains against the full-length \textit{D. melanogaster} proteins in these alignments and measured their overlap with the disorder and order regions. The results show a clear enrichment in the disorder regions having no or only small amounts of overlap relative to the order regions, indicating that, relative to structured domains, IDRs are especially resistant to homology-based methods of functional annotation (Fig.~\ref{sfig:pfam}).

@@

\subsection{Future evolutionary analyses of IDRs will require a multimodal approach}
As discussed by Zarin \textit{et al.}, the interpretation of evolutionary signatures is complicated by several methodological limitations~\cite{Zarin2019}. For example, because IDRs are identified as contiguous segments of high predicted disorder, their boundaries are defined by adjacent structural elements. This approach can therefore split an IDR that is a single evolutionary or functional unit if it contains a semi-disordered module that scores below the threshold. Conversely, it can also merge two distinct IDRs if they are not separated by at least one folded domain.

% TODO: Expand with more discussion for consequences of ``fuzzy'' boundaries on feature calculations
% Inclusion regions in alignments can create signals of conserved features
% Not incorrect, but not a biologically interesting insight
% More targeted applications of this framework where investigators choose boundaries of interest for specific IDRs or exclude conserved sub-regions can ensure the results are directly related to the rapidly evolving regions of IDRs.

Another challenge is the significant overlap in the definitions of many features induces strong correlations that preclude straightforward quantitative manipulations or interpretations of an IDR's evolutionary signature. The original authors have since addressed this in subsequent studies by applying machine learning methods to perform feature selection or learn features directly from alignments of IDRs~\cite{Zarin2021, Lu2022}. However, integrating these methods into a unified phylogenetic comparative framework will require further effort.
